Parsing Tweets into Universal Dependencies

### 2017-11-26 paper.tex
add tokenization section

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
\newcommand{\yicomment}[1]{\textcolor{red}{[#1 ---\textsc{nas}]}}

@@

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachements. 
It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweets treebank ({\sc Tweebank})
which has 12,149 tokens and largely followed the conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
\citet{Yamada03statisticaldependency} dependencies. Both these
annotation efforts were highly influenced by the PTB whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweets treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which wasn't
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.
We characterize the disagreement among our annotations and show that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show an improvement of more
than 2.3 points in LAS over baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

Contribution of this paper includes:
\begin{itemize}
\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
and create a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.
We also characterize the difficulties of creating such annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
method in training the parser in our pipeline which achieve 2.3 points improvement
without sacrificing efficiency and outperform other state-of-the-art parsers
in our comparison.
\end{itemize}

@@

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}
\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}

In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
Then we introduce the difference in our part-of-speech (re)annotation with 
\citet{gimpel-EtAl:2011:ACL-HLT2011} which {\sc Tweebank v1} was built 
on (\S\ref{sec:pos-anno}). Then, we move to our efford of adopting the
UD convention to cover tweets specific constructions. At last, we describ
our process of creating new tweet treebank and characterize
the difficulties in reaching consistent annotations.
\nascomment{need to introduce this section and explain the structure.}
\yjcomment{done.}

@@

The annotation effort we describe stands in contrast to previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added a layer to a portion of the data
annotated with part-of-speech tags by
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  They also contributed a system
for parsing;
we defer discussion of their parser to \S\ref{sec:parsing}.

Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by non-native speakers, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic.''
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}

Before turning to UD annotations, we (re)annotated the data with 
part-of-speech, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}

@@

Compared to coarse-grained part-of-speech tagging effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed the rule-based
system  introduced by 
\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only accounted for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 840 unique tweets, including training and test set), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016.
The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM postagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
\end{figure}

>>>>

\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
\newcommand{\yicomment}[1]{\textcolor{green}{[#1 ---\textsc{Yi}]}}

@@

\begin{document}
\maketitle
\begin{abstract}
In this paper, we study the problem of analyzing tweets with
universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Under such guidelines, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachments.\yicomment{labelled attachments}
It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. \yicomment{unlabelled attachments for the original Tweebank}
We characterize the disagreements
among our annotation and show that it is challenging to deliver
consistent annotation due to the ambiguities in ways of
understanding and explaining the tweets. Over the new treebank,
we build a pipeline system to parse raw tweets into UD. To conquer the
annotation noise without sacrificing efficiency, we propose a new
method to distill an ensemble of 20 parsers into a single one. Our
parser achieves an improvement of 2.3 in LAS over the baseline
and outperforms other state-of-the-art parsers.
\end{abstract}

\section{Introduction}
Analyzing the syntax of tweets is challenging. The challenges not
only come from the difficulty of adapting the parser trained on the
standard text to the Twitter domain, but also comes from creating
reasonable dataset for training and evaluating tweet parsers. 
\citet{AAAIW113912} pioneered in this research direction by
annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
constituencies to a set of tweets which contains 7,630 tokens. 
Stanford dependencies were converted afterwards. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank})
which has 12,149 tokens and largely followed the conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
\citet{Yamada03statisticaldependency} dependencies. 
Both annotation efforts were highly influenced by the PTB, whose guideline
has a good grammatical coverage on newswire. However, when it comes
to the noisy and informal user generated text, it's questionable
whether such good coverage holds.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptive to different genres and languages
\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we create a new tweet treebank of 55,607 tokens by following the UD
guidelines but also contending the domain-specific challenges which were not
covered by UD guidelines. Our annotation includes a whole pipeline of
tokenization, part-of-speech (POS) tags and universal dependencies.
We characterize the disagreement among our annotations and show that
consistent annotation is still challenging to deliver even with
the extended guidelines.

@@

To conquer the noise in our annotation and achieve better performance
without sacrificing efficiency, we propose a new method to
train the parser with the distillation 
\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
We show that learning from the exploration of the ensemble parser
can be more beneficial than just learning from the gold standard
transition sequence in the sense of training a transition-based
distilling parser. Experimental results show that an improvement of more
than 2.3 points in LAS over baseline parser can be achieved with our
distillation method and it outperforms other state-of-the-art parsers.

Contribution of this paper includes:
\begin{itemize}
\item We studied the challenges of annotating tweets in UD (\S\ref{sec:anno})
and created a new tweet treebank ({\sc Tweebank v2}), which includes 
tokenization, part-of-speech tagging, and dependencies annotation.
We also characterized the difficulties of creating such annotation.

\item We built up a whole pipeline to parse the raw tweet text into
universal dependencies (\S\ref{sec:parsing}). We proposed a new distillation
method in training the parser in our pipeline which achieve 2.3 points improvement in LAS
without sacrificing efficiency and outperformed other state-of-the-art parsers
in our comparison. \yicomment{change verbs to past tense}
\end{itemize}

@@

\nascomment{I didn't do anything significant to the intro.  for every
  example, make clear whether it's ``real'' or contrived.}
\yjcomment{I've add the source of our example in the figure caption.}
\section{Annotation}\label{sec:anno}
\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
Then we introduce the difference in our tokenization and part-of-speech (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011} on which {\sc Tweebank v1} was built (\S\ref{sec:pos-anno}). \yicomment{add tok} 
Then, we move to our effort of adopting the
UD conventions to cover tweet specific constructions. 
At last, we describe our process of creating new tweet treebank and characterize
the difficulties in reaching consistent annotations.
\nascomment{need to introduce this section and explain the structure.}
\yjcomment{done.}

@@

The annotation effort we describe stands in contrast to previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added dependencies to a portion of the data
annotated with POS tags by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT} after tokenization \citep{ICWSM101540} \yicomment{add tok}.  
They also contributed a system for parsing;
we defer the discussion of their parser to \S\ref{sec:parsing}.

\citet{kong-EtAl:2014:EMNLP2014}'s rapid, small-scale annotation effort was heavily constrained.  It was
carried out mostly by non-native speakers, in a very short amount of
time (a day).  Driven both by the style of the text they sought to annotate
and by exigency, some of their annotation conventions included:
\begin{itemize}
\item Allowing an annotator to exclude tokens from the dependency
  tree.  A clear criterion for exclusion was not given, but many
  tokens were excluded because they were deemed ``non-syntactic.''
\item Allowing an annotator to merge a multiword expression into a
  single node in the dependency tree, with no internal structure.
  Annotators were allowed to take the same step with noun phrases.
\item Allowing multiple roots, since a single tweet might contain more
  than one sentence.
\end{itemize}
These conventions were justified on the grounds of making the
annotation easier for non-experts, but they must be revisited in our
effort to apply UD to tweets.

\subsection{Tokenization}\label{sec:tok-anno}
Our tokenization strategy is in the middle of the strategy of \citet{ICWSM101540} and that of UD. 
We want to fit Twitter texts better in UD dependencies while preserving the original tweets as much as possible.

\citet{ICWSM101540} preserve most of non-informal tokens including 
the hashtags, at-mentions, emoticons \& emojis and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD tokenization\footnote{http://universaldependencies.org/u/overview/tokenization.html\yicomment{is it ok? no paper reference but webpage reference}} , in order to serve better dependency annotation, treat each syntactic word as token.
They take more aggressive strategy, including splitting off clitics from contractions or multi-word expressions ({\it gonna}) and combine several orthographic tokens into a single syntactic word. \yicomment{does UD support normalization for acronyms? Did not see it from website, need to check. related to ``idc''}

We do not touch any non-informal token in tweets and leave them as in the original tweets. 
Then we mainly follow UD tokenization. We tokenize contractions and multi-word expressions into their syntactic components, but do not combine tokens that have been already split in the original tweets back anymore.
For example, words like {\it gonna} or {\it can't} will be tokenized to {\it gon na} and {\it ca n't}, and parts like {\it Y O} and {\it R E T W E E T} will be not connected back to single words\footnote{Such tokens only accounts for 0.067\%, and we use {\it goeswith} relation to resolve it.}.

\subsection{Part-of-speech Annotation}\label{sec:pos-anno}

Before turning to UD annotations, we (re)annotated the data with 
POS, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}

@@

Compared to coarse-grained POS tagging effort of
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
matters.  For example, if a token is not considered syntactic by UD
conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
al.~had more extensive conventions).  Other phenomena, like
abbreviations, are more complicated for us, as discussed above;
Gimpel et al.~used a single part of speech for such expressions.

@@

Another important difference is in tokenization.  UD calls for more
aggressive tokenization than that used by
\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed the rule-based
system  introduced by 
\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
contractions and possessives, introducing new parts of speech
instead.\footnote{These tags only account for 2.7\% of tokens,
  leading to concerns about data sparseness in tagging and all
  downstream analyses.}  For us, these tokens must be split, but
universal parts of speech can be applied.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'') \yicomment{`idc' should be discussed in tokenization section, and actually it is already implied from POS section that it should be treated as a single word.}
 and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context.\yicomment{again we should also mention UD tokenization, so might be worth adding a tokenization section}

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
\yicomment{I think it should move to another section, just as in Kong's paper.}
Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (840 unique tweets, 639/201 for training/test set), along with additional 210\yicomment{changed to 210} tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016\footnote{Data downloaded from \url{https://archive.org/}}.
The latter data source consists of 147.4M English tweets after being filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.

%The tweet source of Tweebank V2 consists of three parts. 
%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.  There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set. All of the unique tweets in Tweebank V1 are included in Tweebank V2.
%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total). We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus. The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format. 
%There are xxx tweets in all the streams. We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English. Then we sampled 2500 tweets roughly equally from these months.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
	\yicomment{i'm a little confused by the pic, need discussion}
\end{figure}
